manuscript_figures

### 2024-06-27 scripts/manuscript_figures.Rmd
updated HPI

# Calculate P/B ratio
PB$P_B_ratio <- coefficient * PB$biomass.g.m2^exponent

# Calculate Habitat Productivity Index (HPI)
PB$HPI <- PB$biomass.g.m2 * PB$P_B_ratio

# Aggregate by Transect, Site, Year and calculate mean HPI
hpi_summary <- PB %>%
  group_by(TRANSECT, SITE, YEAR) %>%
  summarise(mean_HPI = mean(HPI))

ggplot(hpi_summary, aes(x = paste(TRANSECT, SITE, sep = " - "), y = mean_HPI, fill = as.factor(YEAR))) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  labs(x = "Transect - Site", y = "Mean Habitat Productivity Index (HPI)") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))

>>>>

# Calculate P/B ratio, the predictive equation is P/B (per year) = 2.64*Wmat^-035 , where Wmat is weight-at-maturity (Randall and Minns 2000)
PB$P_B_ratio <- coefficient * PB$biomass.g.m2^exponent

# Calculate Habitat Productivity Index (HPI), habitat productivity index (HPI), a proposed measure of habitat suitability and productive capacity, can be calculated as the product of average fish biomass and the species P/B coefficient (HPI = B × P/B) (Randall and Minns 2000)
PB$HPI <- PB$biomass.g.m2 * PB$P_B_ratio

# Aggregate by Transect, Site, Year and calculate mean HPI
hpi_summary <- PB %>%
  group_by(TRANSECT, SITE, YEAR) %>%
  summarise(mean_HPI = mean(HPI, na.rm = TRUE))

# Make faceted line plot of HPI index over the years
hpi.plot < - ggplot(hpi_summary, aes(x = interaction(TRANSECT, SITE, sep = " - "), y = mean_HPI, fill = as.factor(YEAR))) +
  geom_bar(stat = "identity", position = "dodge", color = "black") +
  labs(x = "Transect - Site", y = "Mean Habitat Productivity Index (HPI)", fill = "Year") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1));hpi.plot
